Tables and Figures - Supplement A, B and C

### 2019-12-16 code/06_Supplement-tables-figures.Rmd
Dropped Panel C from Supplement A

```{r load packages, data and source functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(kableExtra)){install.packages("kablExxtra")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(cowplot)){install.packages("cowplot")}
if(!require(boot)){install.packages("boot")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(ggplot2) #plotting figures
library(cowplot) #combine plots
library(kableExtra) #create fancy pdf tables
library(boot) #Bootstrap confidence intervals for correlations

@@

```{r c-plot-1, cache = FALSE}
c_plot <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + 
  geom_point() + 
  scale_y_continuous(name = "Tau") +
  scale_x_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  ggtitle("Point-Biserial r (transformed SMD)")

@@

```{r, fig.width = 6, fig.asp = 1.3}
cowplot::plot_grid(a_plot, b_plot, c_plot, ncol = 1, labels = "AUTO")

@@

_Figure S.1_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1. Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text). Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations. Panel C  shows the associations between estimates of $I^2$ on the SMD metric and estimates of $\tau$ after transformation.

>>>>

```{r load packages, data and source functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(kableExtra)){install.packages("kablExtra")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(cowplot)){install.packages("cowplot")}
if(!require(ggrepel)){install.packages("ggrepel")}
if(!require(boot)){install.packages("boot")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(ggplot2) #plotting figures
library(cowplot) #combine plots
library(ggrepel) #easy labels for plots (supplement A identification of points)
library(kableExtra) #create fancy pdf tables
library(boot) #Bootstrap confidence intervals for correlations

@@

@@

```{r, fig.width = 6, fig.asp = 1.3}

cowplot::plot_grid(a_plot, b_plot, ncol = 1, labels = "AUTO")

@@

_Figure S.1_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1. Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text). Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations.

```{r text-results, eval = FALSE}
#Not printed if knitting the document.

#to find out which point is which effect in Panel B. 
b_plot + ggrepel::geom_label_repel(data = b, aes(label = effect))

#Examine effects of larger effect size on transformation
transform_d_to_r(c(0, 0.1, 1, 1.1, 2, 2.1), n1 = 100, n2 = 100) #sourced function

#to find out which point is which effect in Panel c. 
c_plot + ggrepel::geom_label_repel(data = d, aes(label = effect))
